Data-Driven Search-based Software Engineering

### 2018-01-24 doc/tex/msr18/main.tex

@@

\begin{document}
\title{
% Research and Teaching Tools for 
Resources for Data-Driven Search-Based SE}
% \titlenote{Produces the permission block, and
%   copyright information}
% \subtitle{Extended Abstract}
% \subtitlenote{The full version of the author's guide is available as
%   \texttt{acmart.pdf} document}

@@

\begin{abstract}
This paper introduces tiny.cc/sbse, a  new shared resource for the Mining Software
Repositories (MSR) community.
The resource contains 89
artifacts related to data-driven search-based SE.
These artifacts are divided into 13 groups
such as requirements engineering, software product lines, software processes, etc.
Artifacts come with   meta-data about what papers have used 
the artifacts   in the past.

This paper describes that resource,    how to use it,
and why the general MSR community might find it insightful.
The resource is a Github repository and our intent is that it
attracts enough attention that  other researchers  clone, modify, the submit  pull requests. In this way, we hope it grows
into a widely-used MSR resource.
\end{abstract}

@@

\begin{figure*}[!t]
{\center
\includegraphics[width=5.5in]{img/page1.png}}
\caption{Our Github-based repository  for resources relating to data-driven Search-based SE.
http://tiny.cc/sbse}\label{fig:one}
\end{figure*}

@@

The MSR  community has benefited enormously from widely shared data sets.  Such data sets document the canonical problems in a field.
They serve to cluster together like-minded researchers while  
  allowing   them to generate reproducible results. Also, such data can be used by
   newcomers to learn state-of-the-set methods in this field. Further, they enable the mainstay of good science:
reputable, repeatable,  improvable, and even refutable results.
At the time of this writing,   nine of the 50 most cited papers in the last 5 years at IEEE Transactions of Software Engineering all draw their case studies
from a small number of similar defect prediction data sets.

@@

There has been a recent increased in methods that combine MSR and SBSE.
A recent workshop  on {\em Data-drive Search-based Software
Engineering} (goo.gl/f8D3EC)   was well attended by over two dozen senior members of the MSR community.
The workshop concluded that (1) the mining software repositories can be improved using search-based methods; and that (2) search-based methods can be improved using tools from the MSR community. 
For example:
\begin{itemize}
\item
MSR data mining algorithms can be used to summarize the data, after which SBSE can leap to better solutions, faster~\cite{krall2015gale}.
\item
SBSE tools can be used to intelligently select 
settings for MSR data mining algorithms (e.g.
such as how many trees should be included in a random
forest~\cite{fu2016tuning}).
\end{itemize}
One result of that workshop was a call for more resources that can be used by researchers and educators to better explore MSR+SBSE.
In response to that call,  this paper describes http://tiny.cc/sbse,
a collection of artifacts for exploring
data-driven search-based SE (see Figure~1). 
 Each artifact  come with meta-data about what papers have used the artifacts in the past. Hence, each artifact can be viewed as a challenge problem: i.e. can you repeat/ improve/ refute prior results that used this artifact?

It has    taken several years to build this resource. Prior to its
existence, we explored  data-driven search-based SE
prototypes on tiny toy tasks that proved 
uninteresting to 
 reviewers from SE venues.

Recently we have much more success in terms of novel.
research results
(and publications at SE forums) after 
expanding that collection
to include models
of (e.g.) software product lines, requirements, and
agile software projects. 
As such we have found it to be a very useful resource
which we now offer to the MSR community.

@@

\section{What is Different About SBSE?}

The following  attempts to list
some of the main differences between MSR and SBSE.
To  misquote George Box, we hope this list is
 more useful than 
wrong

In MSR,  data is often collected then processed.
In SBSE,  data is collected on demand
from  some generator-- which means an SBSE analysis can easily
generate new samples of the data in very small specific regions.

Canonical MSR tools are usually collections of
data mining algorithms such as the decision
tree learners of WEKA~\cite{xx} or the mathematical modeling tools of R~\cite{xx}.
Canonical MSR tools are mulit-objective optimization algorithms which may be either home-grown scripts or parts of large toolkits like jMETAL/DEAP used by JAVA/PYTHON programmers (respectively)~\cite{refs2jmetalDEE}.

Canonical MSR problems include defect prediction~\cite{lessmann2008benchmarking}   or Stackoverflow text mining~\cite{fu2017easy}. 
Canonical SBSE problems include configuring a software system~\cite{nair2017faster} or extracting a valid(ish) product from a product line description~\cite{sayyad13b} or minimizing a test suite~\cite{fraserXXX} or selecting screen designs that
reduce the power consumption  mobile devices

Results obtained from
MSR tools are assessed by a small number of standard measures
including   recall, precision, or false alarm rates (for discrete classes)
or magnitude of relative error or standardized error~\cite{Shepperd2012}.
Results obtained from SBSE tools are assessed by a wide-variety of domain-specific objectives-- indeed those objectives are defined before the SBSE
runs and are used to guide the inference of the SBSE tool.
What ever the specific objectives, a small number meta-measures are used in many research papers such as the hypervolume or spread (which are ways to characterize how well an SBSE tool explores a space of objectives).

@@

\section{Synergies between MSR and SBSE}

To motivate the rest of this paper, we first answer the basic question: why would anyone in the MSR
community ever need to explore SBSE?

 To answer this question, we note that
 software engineering tasks rarely involve a
single goal. For example, when a software engineer
is testing a software, she may be interested in
finding the highest possible number of software
defects at the same time as minimizing the time
required for testing. Similarly, when a software
engineer is planning the development of a software,
he/she may be interested in minimizing the number of
defects, the effort required to develop the software
and the cost of the software. The existence of {\em
multiple goals} and {\em multi-objective optimizers}
thus profoundly affects data science for software
engineering.

So far, the existence of multiple goals/objectives
has been studied more in search-based software
engineering than in the MSR community (exceptions: TIMM,diPenta,Minku). We think that will change, very
soon. In the very near future, we foresee a stronger
emphasis on multiple goals in data science for
software engineering.

In software engineering, biases are expressed as the {\em values}
business users espouse for a system.
 Barry Boehm~\cite{boehm04}
advocated assessing
software development technologies
 by the {\em value} they give
to particular stake-holders. Note that this is
very different to standard practice (which assesses technologies
via their functionality).

In his description of value-based SE, Boehm favors
continuous optimization methods to  conduct cost/benefit
trade-off studies. Translated into the terminology
of this book, he is advocated data mining methods that are
tuned to different value proposition.

A problem with this kind of trade-off is that it must explore some
underlying space of options.  In a conventional approach, some
business process model could be developed, then exercised many
times. Such a {\em data farming} approach: 
\begin{itemize}
\item
{\em Plants a seed.} Build a model from domain information. All uncertainties or missing parts of the domain information are modeled as a space of possibilities.
\item {\em Grows the data.} Execute model and, when the model moves into the space of possibilities, output is created by selecting at random from the possibilities.
\item {\em Harvests.} Summarize the grown data via data mining.
\item Optionally, use the harvested summaries to improve the model;
  then, go to 1. 
\end{itemize}

  While these two terms have many differences, they relate to a similar concept:
\begin{enumerate}
\item Tuning instability refers to uncertainties inside a model;
\item Value variability refers to uncertainty on how to assess the outputs of a model.
\end{enumerate}
Our reading of the software engineering literature is that most papers only explore
a small subset of Figure 23.1 or Figure 23.2. We think this is a mistake and researchers
should more to a more general framework where they explore a wide and changing set
of evaluation criteria. The next section describes one such framework.
23.2.2.3 Exploring Instability and Variability
To address the above problems, we adopt two strategies:
\begin{itemize}
\item  To address value variability we:
\begin{itemize}
    \item Use tools that allow for the customization of the value proposition used to
    guide the search.
    \item Then run the models using different value propositions.
\end{itemize}
\item To address tuning instability we:
\begin{itemize}
    \item Determine the space of known tunings for a model;
    \item Allow models to range over that space;
    \item Extensively simulate the models;
    \item Look for stable conclusions over the entire space of tunings.
\end{itemize}
\end{itemize}
The rest of this chapter offers an example of this kind of analysis

\begin{figure}[!b]
\small
\begin{tabular}{p{.95\linewidth}}\hline
\rowcolor{gray!10}
Let $\{A,B,C,D\}$ denote the
true negatives,
false negatives,
false positives, and
true positives
(respectively) found by a software defect detector.
Also, let $L_A L_b, L_c, L_d$ be the lines of code
seen in the parts of system that fall
into $A,B,C,D$. Then:
\[
\begin{array}{r@{~}l}
\mathit{pd}=\mathit{recall}=&D / (B+D)\\
\mathit{pf}=&C / (A+C)\\
\mathit{prec}=\mathit{precision}=&D / (D+C)\\
\mathit{acc}=\mathit{accuracy}=&(A+D) / (A+B+C+D)\\
\mathit{support}=&(C+D) / (A+B+C+D)\\
\textit{effort}=&(L_c+L_d) / (L_a + L_b + L_c + L_d)\\
\mathit{reward}=&\mathit{pd} / \textit{effort}
\end{array}
\]\\\hline
\end{tabular}
\caption{Some assessment criteria widely used in MSR.}\label{fig:criteria}
\end{figure}

@@

\begin{tabular}{p{.95\linewidth}}\hline 
\rowcolor{gray!10}
Some goals relate to aspects of defect prediction:
\begin{enumerate}[leftmargin=0.4cm]

>>>>

\usepackage{array}

\newcommand{\calcfactor}[1]{%
  \dimexpr#1\textwidth-2\tabcolsep-1.5\arrayrulewidth\relax
}
\newcolumntype{P}[1]{p{\calcfactor{#1}}}

@@

\begin{document}
\title{Data-Driven Search-based Software Engineering}
% \titlenote{Produces the permission block, and
%   copyright information}
% \subtitle{Extended Abstract}
% \subtitlenote{The full version of the author's guide is available as
%   \texttt{acmart.pdf} document}

@@

\begin{abstract}
This paper introduces ideas and resources for a new field of software engineering research: Data-Driven Search-based software Engineering (DSE), which includes insights from Software Analytics (SA) and Search-based Software Engineering (SBSE). The paper argues that these domains within Software Engineering should not work in isolation but exchange ideas among them. Such techniques can be particularly useful for situations which require learning from a lot of data or optimizing problems which need resources.

This paper also presents resources (tiny.cc/sbse) and reports on our experience of tackling various SE problems.  The resource contains 89 artifacts related to data-driven search-based SE. These artifacts are divided into 13 groups such as requirements engineering, software product lines, software processes, etc. (and each artifact is related to a paper(s) that have used it).

Among the numerous questions that we try to answer are: (1) What are the various topics addressed by DSE?, (2) What are the types of data used by the researchers, and, (3) What research approaches do researchers use? The paper briefly sets out to act as a practical guide to develop new data-driven techniques and also to serve as a teaching resource.
\end{abstract}

@@

\begin{figure}[!b]

{\center
\fbox{ \includegraphics[width=3.3in]{img/page1.png}}}
\caption{http://tiny.cc/sbse}\label{fig:one}
\end{figure}

@@

The MSR  community has benefited enormously from widely shared datasets.  Such datasets document the canonical problems in a field.
They serve to cluster together like-minded researchers while  
  allowing   them to generate reproducible results. Also, such data can be used by
   newcomers to learn state-of-the-art methods in this field. Further, they enable the mainstay of good science:
reputable, repeatable,  improvable, and even refutable results.
At the time of this writing,   nine of the 50 most cited papers in the last 5 years at IEEE Transactions of Software Engineering all draw their case studies
from a small number of similar defect prediction datasets.

@@

\begin{figure*}
    \centering
\small
\colorbox{gray!20}{
\begin{tabular}{@{}p{3cm}p{6cm}p{8.35cm}@{}}
\multicolumn{3}{c}{\rowcolor{gray}\textcolor{white}{\textbf{Problems in Search-based Software Engineering}}} \\ 
\multicolumn{3}{c}{
		\begin{minipage}[b]{0.33\linewidth}
			\begin{flushleft}
				\includegraphics[height=4.6cm]{doc/tex/msr18/img/pareto.png}
				% \vspace{8pt}
			\end{flushleft}
		\end{minipage}\hspace{0.1cm}
		\begin{minipage}[b]{0.63\linewidth}
		        \textbf{Problem: } SBSE converts a SE problem into an optimization problem, where the goal is to find the maxima or minima of a function $y=f(x)$. , where x is called the \textit{independent variable}, $f$ is the evaluation function, and $y$ the \textit{dependent variable}.\\
		        \textbf{Problem Types: } The problems can be either single-~\cite{nair2017faster} or multi-~\cite{chen2017sampling} or many-objective~\cite{mkaouer2014high}.\\
		        \textbf{Global Maxima/Minima: } For single objective problems, there is one global mixima or minima.\\
		        \textbf{Pareto Front: } For multi- and many-objective problems, there no single `best' solution instead there are number of `best' solution. The best solutions are found using a \textit{dominance} relation.\\
		        \textbf{Dominance: }The domination criterion  can be defined as: ``A solution $x_1$ is said to dominate\\
                another solution $x_2$, if $x_1$ is no worse than $x_2$ in all objectives
                and $x_1$ is strictly better than $x_2$ in at least one objective.''\\
		        \textbf{Actual PF: } A list of best solutions of a space is called Actual PF ($a\in A$). This requires knowledge of the whole space---which is not available in real-world setting.\\
		        \textbf{Predicted PF: } The solutions found by a meta-heuristic algorithm is called the Predicted PF ($p\in P$).
				%  Problems tacked in SBSE can be described as finding the best (minimum or maximum) of a function ($y=f(x)$), where x is called the \textit{independent variable}, $f$ is the evaluation function, and $y$ the \textit{dependent variable}. $y$ can either be single objective or multi-objective. In a multi-objective setting, there no single `best' solution instead there is number of `best' solution. This can also be stated as solutions which are better (or \textit{dominates}) all other solution---which is not considered `best' solutions, and no better than other `best' solution as defined by domination criterion. The domination criterion  can be defined as: ``A solution $x_1$ is said to dominate
    %             another solution $x_2$, if $x_1$ is no worse than $x_2$ in all objectives
    %             and $x_1$ is strictly better than $x_2$ in at least one objective.'' The list of these `best' solutions are called the \textit{Pareto Front}. The figure represents a solution space of a (synthetic) multi-objective problem with two objectives: $\mathit{Objective}_1$ and $\mathit{Objective}_2$. This best point can be called as the \textit{Utopia Point} and the worst is called the \textit{Nadir Point}. The points $A_i$ represents the \textit{Actual Pareto Front} ($A$). The goal of the multi-objective optimizer is to find set of solutions which are closest to the actual Pareto frontier. The solutions found by the optimizers are called the \textit{Predicted Pareto Front} ($P$). \vspace{0.1cm}
		\end{minipage}

} \\ 
\multicolumn{3}{c}{\rowcolor{gray}\textcolor{white}{\textbf{Components of Meta-heuristic Algorithms (such as NSGA-II~\cite{deb2000fast}, SPEA2~\cite{zitzler2001spea2}, MOEA/D~\cite{zhang2007moea})}}} \\
\multicolumn{3}{c}{
\begin{minipage}[b]{\linewidth}
\vspace{0.1cm}
\noindent\textbf{Data Collection or Model building: } SBSE process can either rely on a model, which represent a software process~\cite{boehm1995cost} or can be directly applied to any software engineering problem including problems which requires evaluating a solution by running a specific benchmark~\cite{krall2015gale}.

\noindent\textbf{Representation: } The process of search starts by creating random solutions (valid or invalid) of certain problems~\cite{saber2017seeding, chen2017beyond, chen2017sampling, henard2015combining}. 
The representation of these solutions is significant to generate the landscape of the problem. The general representation of the problem uses either boolean or numerics. This representation can also be called as the \textit{Decision Space}.

\noindent\textbf{Fitness Function: } A fitness function maps the solution (which is represented using numerics) to a numeric scale (also called as \textit{Objective Space}) which is used to distinguish between good and not so good solutions. This measure is a domain-specific measure (single objective) or measures (multi-objective) which is useful for the practitioners.
% Examples of various fitness used in SBSE are (i) difference between the lowest and the highest number of transformation elements~\cite{fleck2017model} or (ii) number of test cases passed~\cite{oliveira2016improved}. 
% The fitness function determines the fitness landscape of the problem---which characterizes the problem and defines the `hardness' of the problem.
% Fitness landscape should not be too flat, which means the meta-heuristic algorithms cannot find the best possible direction to explore. 
Simply put fitness function is a transformation function which converts the point in the decision space to an objective space.

\noindent\textbf{Operators: } Meta-heuristic algorithms require \textit{recombination operators} such as crossover and mutation operators which can be applied along with \textit{elitism operator} to simulate the `survival of the fittest' strategy. The combination operator combines the features of various solutions in the population to generate new candidates. The elitism operator uses these fitness values to eliminate the not so good solutions from the population. 
\end{minipage}
}
 \\
\multicolumn{3}{c}{\rowcolor{gray}\textcolor{white}{\textbf{Performance Measures (Refer to \cite{wang2016practical} for more detail)}}} \\ 
% \multicolumn{2}{c}{\textbf{SA}} & \textbf{SBSE} \\ \midrule
\multicolumn{3}{c}{
% \begin{minipage}[b]{0.5\linewidth}
% Let $\{A,B,C,D\}$ denote the
% true negatives,
% false negatives,
% false positives, and
% true positives
% (respectively) found by a software defect detector.
% Also, let $L_A L_b, L_c, L_d$ be the lines of code
% seen in the parts of system that fall
% into $A,B,C,D$. Given these definitions then

% {\small\[
% \begin{array}{r@{~}l}
% \mathit{\textbf{pd}}=\mathit{\textbf{recall}}=&D / (B+D)\\
% \mathit{\textbf{pf}}=&C / (A+C)\\
% \mathit{\textbf{prec}}=\mathit{\textbf{precision}}=&D / (D+C)\\
% \mathit{\textbf{acc}}=\mathit{\textbf{accuracy}}=&(A+D) / (A+B+C+D)\\
% \mathit{\textbf{support}}=&(C+D) / (A+B+C+D)\\
% \textit{\textbf{effort}}=&(L_c+L_d) / (L_a + L_b + L_c + L_d)\\
% \mathit{\textbf{reward}}=&\mathit{pd} / \textit{effort}
% \end{array}
% \]}.
% \end{minipage}\hspace{0.1cm}

\begin{minipage}[b]{0.3\linewidth}
\includegraphics[height=2.5cm]{doc/tex/msr18/img/gd.png}
\includegraphics[height=2.5cm]{doc/tex/msr18/img/igd.png}
\includegraphics[height=2.5cm]{doc/tex/msr18/img/hv.png}
\includegraphics[height=2.5cm]{doc/tex/msr18/img/spread.png}

\end{minipage}

\begin{minipage}[b]{0.7\linewidth}
\vspace{0.1cm}
\noindent\textbf{Generational Distance: } Generational distance is the measure of convergence---how close is the predicted Pareto front is to the actual Pareto front. It is defined to measure how far are the solutions that exist in $P$ from the nearest solutions in $A$. The Generational Distance can be defined as $GD = \frac{\sqrt{\sum_{0}^{|P|} \mathit{dist}(p, a)^2}}{|P|}$.%, where $p\in P$ and $a\in A$.

\noindent\textbf{Spread: } Spread is a measure of diversity---how well the solutions in P are spread. An ideal case is when the solutions in P is spread evenly across the Predicted Pareto Front. The spread is defined as 
$\mathit{Spread}=\frac{\sum_{1}^{|e_k|} {d(e_k, P) + \sum_{0}^{P} |d(p,P)-\overline{d}|}}{\sum_{1}^{|e_k|} d(e_k, P) + |P|*\overline{d}}$ 
where $e\in E$ refers to m ($|E|$) extreme solutions for each objective in the problem.

\noindent\textbf{Inverted Generational Distance: } Inverted Generational distance measures both convergence as well as diversity of the solutions---measures the shortest distance from each solution in A to the closest solution in P. The Inverted Generational Distance can be defined as $IGD = \frac{\sqrt{\sum_{0}^{|A|} \mathit{dist}(p, a)^2}}{|A|}$.%, where $p\in P$ and $a\in A$.

\noindent\textbf{Hypervolume: } Hypervolume measures both convergence as well as diversity of the solutions---measure the volume in the
objective space that is covered by Pareto optimal points (either P or A).

\end{minipage}	
}\\
\multicolumn{3}{c}{\rowcolor{gray}\textcolor{white}{\textbf{Differences between Software Analytics and Search-based Software Engineering}}} \\ 
 \underline{\textbf{Features}} & \hspace{2cm}\underline{\textbf{SA}} & \hspace{3cm}\underline{\textbf{SBSE}} \\ 
 \rowcolor{gray!40} \textbf{Primary inference} & Induction, summarization, visualization & Optimization \\
\textbf{Inference speed} & Very fast, scalable & Becoming faster, more scalable\\
 \rowcolor{gray!40}\textbf{Data} often collected &
 Once,  then processed.
&
On-demand
from  some model---which means an SBSE analysis can 
generate new samples of the data in very  specific regions.
\\ 
\textbf{Conclusions} often 
generated via
&
A single  execution of a data miner
(perhaps with some data pre-processing). 
&
An evolutionary process  where execution $i+1$ is guided
by the results of execution $i$.
\\

 \rowcolor{gray!40}\textbf{Canonical   tools} are usually
&
Data mining algorithms like  the decision
tree learners of WEKA~\cite{hall2009weka} or the mathematical modeling tools of R~\cite{rmanual18}.
&
Multi-objective optimization algorithms which may be either home-grown scripts or parts of large toolkits like jMETAL/DEAP used by Java/Python programmers (respectively)~\cite{refs2jmetalDEE, DEAP_JMLR2012}.
\\ 
\textbf{Canonical   problems}
&
Defect prediction~\cite{lessmann2008benchmarking}   or Stackoverflow text mining~\cite{fu2017easy}. 
&
Configuring a software system~\cite{nair2017faster} or extracting a valid products from a product line description~\cite{sayyad13b} or minimizing a test suite~\cite{fraser2007redundancy}
% or selecting screen designs that
% reduce the power consumption  mobile devices
\\

 \rowcolor{gray!40} \textbf{Results}   assessed by
&
A small number of standard measures
including   recall, precision, or false alarm rates (for discrete classes)
or magnitude of relative error or standardized error (for continious classes)~\cite{Shepperd2012}.
&
A wide-variety of domain-specific objective.
What ever the specific objectives, a small number meta-measures are used in many research papers such as the Hypervolume or Spread. 
\end{tabular}}
\caption{A tutorial on Search-based Software Engineering.}
\label{fig:sbse_crash}
\end{figure*}
% \begin{figure*}
% { \small
% \begin{tabular}{lp{.26\linewidth}p{.48\linewidth}}
%  \rowcolor{gray} & \textcolor{white}{{\bf MSR}} & \textcolor{white}{{\bf SBSE}}\\ 
%  \textbf{Primary inference} & induction, sumamrization, visualiztion & optimization \\
%  \rowcolor{gray!20}\textbf{Inference speed} & very fast, scalable & becoming faster, more scalable\\
% \textbf{Data} often collected... &
% ... once,  then processed.
% &
% ... on demand
% from  some generator-- which means an SBSE analysis can 
% generate new samples of the data in very  specific regions.
% \\ 
% \rowcolor{gray!20}
% \textbf{Conclusions} often 
% generated via...
% &
% ...a single  execution of a data miner
% (perhaps with some data pre-processing). 
% &
% ...an evolutionary process  where execution $i+1$ is guided
% by the results of execution $i$.
% \\

% \textbf{Canonical   tools} are usually ..
% &
% ... data mining algorithms like  the decision
% tree learners of WEKA~\cite{hall2009weka} or the mathematical modeling tools of R~\cite{rmanual18}.
% &
% ... multi-objective optimization algorithms which may be either home-grown scripts or parts of large toolkits like jMETAL/DEAP used by JAVA/PYTHON programmers (respectively)~\cite{refs2jmetalDEE, DEAP_JMLR2012}.
% \\ 
%  \rowcolor{gray!20}
% \textbf{Canonical   problems} include...
% &
% ...defect prediction~\cite{lessmann2008benchmarking}   or Stackoverflow text mining~\cite{fu2017easy}. 
% &
%  ...configuring a software system~\cite{nair2017faster} or extracting a valid(ish) product from a product line description~\cite{sayyad13b} or minimizing a test suite~\cite{fraser2007redundancy} or selecting screen designs that
% reduce the power consumption  mobile devices
% \\

% \textbf{Results}   assessed by....
% &
% ...a small number of standard measures
% including   recall, precision, or false alarm rates (for discrete classes)
% or magnitude of relative error or standardized error~\cite{Shepperd2012}.
% &
% ... a wide-variety of domain-specific objective.
% What ever the specific objectives, a small number meta-measures are used in many research papers such as the hypervolume or spread (which are ways to characterize how well an SBSE tool explores a space of objectives). \\
% \hline
% \end{tabular}}
% \caption{Some differences between MSR and SBSE. To  misquote George Box, we hope this list is  more useful than  wrong.}\label{fig:diff}
% \end{figure*}

There has been a recent increase in methods that combine MSR and SBSE.
A recent workshop  on {\em Data-driven Search-based Software
Engineering} (goo.gl/f8D3EC)   was well attended by over two dozen senior members of the MSR community.
The workshop concluded that (1) the mining software repositories can be improved using search-based methods; and that (2) search-based methods can be improved using tools from the MSR community. 
For example:
\begin{itemize}
\item
MSR data mining algorithms can be used to summarize the data, after which SBSE can leap to better solutions, faster~\cite{krall2015gale}.
\item
SBSE tools can be used to intelligently select 
settings for MSR data mining algorithms (e.g.
such as how many trees should be included in a random
forest~\cite{fu2016tuning}).
\end{itemize}
The workshop also concluded that this community needs more shared  resources 
to help more  researchers and educators   explore MSR+SBSE.
Accordingly, this paper describes  tiny.cc/sbse,
a collection of artifacts for exploring
data-driven search-based SE (see Figure~1). 
It has    taken several years to build this resource. Prior to its
existence, we explored  data-driven search-based SE
prototypes on tiny toy tasks that proved 
uninteresting to 
 reviewers from SE venues. 
Recently we have much more success in terms of novel
research results
(and publications at SE forums) after 
expanding that collection
to include models
of (e.g.) software product lines, requirements, and
agile software projects. 
As such we have found it to be a very useful resource
which we now offer to the MSR community.

@@

@@

\section{What? (Definitions)}

For this paper, we say that MSR covers the technologies
explored by many of the authors at the annual Mining Software Repositories
conference.

As to search-based software engineering, that term was coined by Jones and Harman~\cite{harman2001search} in 2001.
Over the years have been applied to various fields of software engineering for example, requirements~\cite{ZhangHL13, chen2017beyond}, automatic program repair~\cite{le2012genprog}, Software Product Lines~\cite{chen2017sampling, sayyad13a, guo2017smtibea}, Performance configuration optimization~\cite{nair2017faster,nair2017using, guo2017data, oh2017finding, nair2018finding} to name of few. SBSE has been applied to other fields and has their own surveys such as design~\cite{raiha2010survey}, model-driven engineering~\cite{boussaid2017survey}, genetic improvement of programs~\cite{petke2017genetic}, refactoring~\cite{mariani2017systematic}, Testing~\cite{silva2017systematic, khari2017extensive} as well as more general surveys~\cite{clarke2003reformulating, harman2007current}.

 Figure~\ref{fig:sbse_crash} provides a (very) short tutorial on Search-based Software Engineering and  characterizes some the differences between SA and SBSE.

As to defining {\em data-driven search-based SE},
we say it is some system that:
\begin{itemize}
\item To solve  some SE problem:
\begin{itemize}
\item
It inserts  a data miner into an optimizer; or
\item
It uses an optimizer  to improve a data  miner.
\end{itemize}
\end{itemize}

\section{  Why? (Synergies of MSR + SBSE)}

If MSR was completely different to SBSE (as suggested by Figure~\ref{fig:diff}), 
then there would be no point
to this paper. This section argues combining both methods is insightful and useful.

% A recent study by Chen et al.~\cite{xxChenSampleXXX}  illustrates the benefits
% of combining MSR+SBSE. In that study, Chen was applying SBSE 
% to many of the models in tiny.cc/sbse to 
% to optimize   decisions about software processes options, generating product lines,
% and configuring the LINUX kernel. Reviewers of that work requested that his SBSE
% results be compared to some baseline exhaustive search. According, Chen
% generated, then pruned, 10,000 random candidate solutions  using a pairwise comparison procedure.
% These results were compared with state-of-the-art
% SBSE methods that using genetic operators (combine, mutate, select, repeat)
% to carefully explore the same models.

% As expected, the exhaustive search ran impractically slowly (54 hours)
% while the SBSE methods ran two orders of magnitude taster (24 minutes).
% On the other hand,  a statistical comparison showed that the exhaustive approach
% found as good, or better, solutions that the state-of-the-art SBSE
% methods $\frac{44}{48}=92$\% in comparisons.

% This experiment suggests the following exciting possibility.

Consider the following. The MSR
community knows how to deal with large sets of data. The SBSE community knows how to take
clues from different regions of data, then combine them to generate better solutions.
If the two ideas were combined, then  MSR could be  {\em sampling} technology quickly
finds the regions where SBSE  can learn {\em  optimizations}. If so:
\begin{quote}
\centering
{\bf {\em   MSR  methods can ``supercharge''    SBSE.}}
\end{quote}
For a very specific example of this ``supercharging'', consider active learning
with Gaussian Process Models (GPM) used for multi-objective optimization
by the machine learning community~\cite{zuluaga2016varepsilon}.  Active learners assume that evaluating one candidate
is very expensive. For example, in software engineer, ``evaluating'' a test suite
might mean re-compiling
the entire system then re-running all tests. When evaluation is so slow,
an active learner reflects on the example seen so far to find the next most informative
example to evaluate next. One way to do this is to use GPMs  to
find which parts of a model have maximum variance in their predictions 
(since sampling
in such high-variance regions serves to most constrain the model).

The problem with GPMs is that they do not scale beyond a dozen variables (or feaatures)~\cite{wang2016bayesian}. CART, on the other hand, is a data mining algorithm that scales efficiently
to hundreds of variables. So Nair et al. recently explored  
 active learning  for multi-objective optimization by replacing GPM with one CART tree per objective~\cite{nair2018finding}.
 The resulting system was applied to a wide range of software configuration problems
 found in tiny.cc/sbse.
 Compared to GPMs, the resulting system ran orders of magnitude faster, found solutions
 as good or better, and  scaled to much larger problems~\cite{nair2018finding}.

Not only is   MSR useful for   SBSE, but so too:
\begin{quote}
\centering
{\bf {\em SBSE methods can    ``supercharge''    MSR.}}
\end{quote}
The standard example here is parameter tuning. Most data mining algorithms come with tuning
parameters that have to be set via expert judgment. Much recent work shows that for
MSR problems such as defect prediction and text mining, SBSE can automatically find settings that are far superior to the default settings. For example:
\begin{itemize}
 \item
   When performing defect prediction, various groups report that SBSE methods can find new settings that dramatically improve the performance of the learned model~\cite{fu2016tuning,tantithamthavorn2016automated, Tantithamthavorn2018}.

\item When using SMOTE to rebalance data classes, SBSE found that for 
distance calculations using 
  \[d(x,y)=\left(\sum_i(x_i-y_i)^n\right)^{1/n}\] the Euclidean distance of $n=2$ usually works far worse than another distance measure using $n=3$~\cite{agrawal2017better}.

\end{itemize} 
Note that all the above used case study material from tiny.cc/sbse.

% \definecolor{co1}{RGB}{249,239,230}
% \definecolor{co2}{RGB}{255,192,202}
% \definecolor{co3}{RGB}{144,237,144}
% \newcommand{\yy}[1]{\cellcolor{co3} {\textit{#1}}}
% \newcommand{\nn}[1]{\cellcolor{co2} {\textit{#1}}}
% \newcommand{\sAM}[1]{\cellcolor{co1} {\textit{#1}}}
% \begin{figure}[!b]
% {\footnotesize
% \begin{tabular}{rr|c|c|c|c}
% &&\multicolumn{4}{c}{Four multi-objective evaluation criteria}\\\cline{3-6}
% &          & Generational & Generated & Pareto  & Hyper-   \\
% n&model     & Distance     & Spread    & Front Size   & volume    \\\hline
% 1&osp       &    \yy{0.5}          &        \yy{1.95}   &    \yy{0.46}    &     \yy{0.6}       \\
% 2&ops2      &    \yy{1.30}         &     \yy{0.82}      &   \yy{0.72}     &    \yy{0.65}        \\
% 3&ground    &     \nn{0.79}        &      \yy{0.86}     &    \yy{0.71}    &   \sAM{0.30}         \\
% 4&flight    &    \yy{1.96}         &   \yy{0.86}        &     \yy{0.42}     &   \yy{0.52}         \\
% 5&pom3a     &     \yy{0.79}         &   \nn{0.53}         &      \yy{01.30}  &    \yy{0.85}        \\
% 6&pom3b     &        \yy{0.75}     &    \yy{0.43}        &   \yy{0.56}      &  \yy{0.85}           \\
% 7&pom3c     &     \yy{0.69}         &   \yy{0.42}         &     \yy{0.82}    &  \nn{1.03}          \\
% 8&webportal &    \yy{0.63}          & \yy{0.90}          &    \yy{1.86}    &    \sAM{0.63}         \\
% 9&eshop     &    \yy{0.74}         &     \sAM{0.29}      &    \yy{1.23}    &     \yy{1.29}        \\
% 10&fiasco    &      \yy{1.97}       &        \sAM{0.49}    &    \yy{1.99}    &        \sAM{0.23}    \\
% 11&freebsd   &     \yy{0.79}        &      \sAM{0.22}      &    \yy{1.98}    &     \yy{0.63}        \\
% 12&linux     &     \yy{0.72}        &     \sAM{0.13}      &  \yy{1.99}      &        \yy{1.97}    \\\hline
% &same + better& 11/12           & 11/12         & 12/12     & 11/12
% \end{tabular}}
% \caption{{\sc GroundTruth} vs state-of-the-art: How often is ground truth worse, same, or better?
% Summarized from 
% \fig{boxplot}. Color patterns are the same as \fig{boxplot}. Decimal in each cell is the effect size.  Generating and evaluating all the models in this figure took 52 hours of CPU.}\label{fig:sum1}
% \end{figure}
 Yet another, subtler, benefit of combining MSR+SBSE relates to the exploration of competing
 objectives.
 We note that  
 software engineering tasks rarely involve a
single goal. For example, when a software engineer
is testing a software, she may be interested in
finding the highest possible number of software
defects at the same time as minimizing the time
required for testing. Similarly, when a software
engineer is planning the development of a software,
he/she may be interested in minimizing the number of
defects, the effort required to develop the software
and the cost of the software. The existence of {\em
multiple goals} necessarily implies that such problems should be solved via
a   multi-objective optimizers.

There are many such goals. For example, 
let $\{A,B,C,D\}$ denote the
true negatives,
false negatives,
false positives, and
true positives
(respectively) found by a software defect detector.
Also, let $L_A L_b, L_c, L_d$ be the lines of code
seen in the parts of system that fall
into $A,B,C,D$. Given these definitions then

{\small\[
\begin{array}{r@{~}l}
\mathit{pd}=\mathit{recall}=&D / (B+D)\\
\mathit{pf}=&C / (A+C)\\
\mathit{prec}=\mathit{precision}=&D / (D+C)\\
\mathit{acc}=\mathit{accuracy}=&(A+D) / (A+B+C+D)\\
\mathit{support}=&(C+D) / (A+B+C+D)\\
\textit{effort}=&(L_c+L_d) / (L_a + L_b + L_c + L_d)\\
\mathit{reward}=&\mathit{pd} / \textit{effort}
\end{array}
\]}.

@@

\begin{tabular}{p{.95\linewidth}}\hline 
\rowcolor{gray!20}
Some goals relate to aspects of defect prediction:
\begin{enumerate}[leftmargin=0.4cm]
